### 2014-04-08 paper/relatedwork.tex
george comments
shuffle figure around, add in teaser, fix up glamour shots a bit

Previous work has investigated the integration of interactivity with the fabrication process.  Printed Optics (\cite{Willis-printedoptics}) used light pipes, solid clear tubes, to create integrated displays and touch sensors. While the research describes a process, it does not provide a design tool for creating such objects. Our work is inspired by Printed Optics and introduces a design tool for modelling objects that can have these types of capabilities.

Slyper, et al., 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure \cite{Slyper-pressure}.  They created all their models by hand, and were forced to place interaction locations in areas accessible to electronics assembly: this technique is complementary to ours, as we allow placing interactive elements anywhere on an object's surface. Sauron investigated computer vision to track interactions with physical mechanisms \cite{Savage-sauron}.  While Savage, et al., used mirrors for redirection, we believe that the required line-of-sight operation for their computer vision techniques may be possible using printed optics or inserted optical fibers \george{huh?}.

General-purpose routing for connecting 2D capacitive sensors to terminals is discussed in Midas \cite{Savage-midas}.  This technique, based on circuitboard routing, is limited to planar and unfoldable shapes, and intended for use on the surface of objects rather than through their cores.  Fabrickation works towards rapid fabrication of functional objects by integrating construction kit building blocks \cite{Mueller-fabrickation}.  While we recognize that 3D printing requires significant time, we believe creating precise internal structures in 3D printed objects is a strong case for digital fabrication over manual or traditional methods. \george{wording}

@@

Similar to our path routing algorithm, Wong presents a graph-based approach for generating continuous line illustrations from images \cite{Wong-continuousline}. Its approach of linking edges into a continuous line based on semi-Eulerization is similar to ours.  However, we are not confined to the plane to avoid line-crossings, and we can create ``invisible'' lines using \emph{blocking out}\footnote{In neon sign making, segments of a tube that should not appear illuminated are covered with opaque paint. This is called "blocking out". \url{http://en.wikipedia.org/wiki/Neon_sign}} \george{too much detail and talk of our work}. Prior work used tours of nodes, rather than edges, and cast continuous line drawing as a traveling salesman problem~\cite{Bosch-tsp}. In traditional neon sign making, ``routing'' is a conversation between a graphic designer and a glass bender on what is feasible and comfortable for the latter and what will help him avoid burning his hands and wasting time or glass \cite{strattman1997neon}.

>>>>

Previous work has investigated the integration of interactivity with the fabrication process.  Printed Optics \cite{Willis-printedoptics} used light pipes, solid clear tubes, to create integrated displays and touch sensors. While the research describes a process, it does not provide a design tool for creating such objects. Our work is inspired by Printed Optics and introduces a design tool for modelling objects that can have these types of capabilities.

Slyper, et al., 3D printed flexible robot armatures capable of sensing interaction via changes in air pressure \cite{Slyper-pressure}.  They created all their models by hand, and were forced to place interaction locations in areas accessible to electronics assembly: this technique is complementary to ours, as we allow placing interactive elements anywhere on an object's surface. Sauron investigated computer vision to track interactions with physical mechanisms \cite{Savage-sauron}.  While Savage, et al., used mirrors for redirection, we believe that the required line-of-sight for their computer vision techniques may be possible using printed optics or inserted optical fibers \george{huh?}.  General-purpose routing for connecting 2D capacitive sensors to terminals is discussed in Midas \cite{Savage-midas}.  This technique, based on circuitboard routing, is limited to planar and unfoldable shapes, and intended for use on the surface of objects rather than through their cores.

Fabrickation works towards rapid fabrication of functional objects by integrating construction kit building blocks \cite{Mueller-fabrickation}.  While we recognize that 3D printing requires significant time, we believe that precise internal structures in 3D printed objects provide a strong case for digital fabrication over manual or traditional methods.

@@

Similar to our path routing algorithm, Wong presents a graph-based approach for generating continuous line illustrations from images \cite{Wong-continuousline}. Its approach of linking edges into a continuous line based on semi-Eulerization is similar to ours.  However, we are not confined to the plane to avoid line-crossings, and we can create ``invisible'' lines by \emph{blocking out}\footnote{In neon sign making, segments of a path that should not appear illuminated are covered with opaque paint. This is called "blocking out". \url{http://en.wikipedia.org/wiki/Neon_sign}} the inserted media \george{too much detail and talk of our work}. Prior work used tours of nodes, rather than edges, and cast continuous line drawing as a traveling salesman problem \cite{Bosch-tsp}. In traditional neon sign making, ``routing'' is a conversation between a graphic designer and a glass bender on what is feasible and comfortable for the latter and what will help him avoid burning his hands and wasting time or glass \cite{strattman1997neon}.
